Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-07-26 prevalence_testing/postshocktest2022draft.tex
minor changes
changed epsilon notation

We first present some intermediary technical results and definitions. Let $\lambda_{\text{max},\theta_k}$, $\lambda_{\text{max},\theta_\delta}$, $\lambda_{\text{max},\gamma}$ respectively be the largest eigenvalues of $\Sigma_{\theta_k}$, $\Sigma_{\delta}$, and $\Sigma_{\gamma}$ for $k = 1,\ldots,q_2$. Define  
\begin{align*}
  \mu_{\min} &= \min\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\min(\mu_\delta),\min(\mu_{\theta_k}),\min(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \mu_{\max} &= \max\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\max(\mu_\delta),\max(\mu_{\theta_k}),\max(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
  \sigma^2_{\max} &= \max\left(\sigma^2_{\eta},\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_{\alpha},\sigma^2_{\tilde{\phi}_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right),
\end{align*}
and let $\sigma^2 = \max(\lambda_{\max}, \sigma^2_{\max})$. Now fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$ for all $t$ and some choice of $\varepsilon_1$. Pick some large $M > 0$. Fix $T = T_1 = T_{i'}$ and $T^* = T^*_1 = T^*_{i'}$. Define the events 
\begin{align*}
  E_1 := &\left\{\max\left(|\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \varepsilon_1:\right. \\
  &\qquad j = 1,\ldots,q_1, k = 1,\ldots,q_2, t = 1,\ldots,T \left.\right\}, \\
  E_2 := &\{\|(\bm{\eta}',\bm{\phi}',\bm{\theta}',\bm{\delta}',\tilde{\bm{\phi}}',\tilde{\bm{\theta}}')'\|_\infty < M_1\},  
\end{align*}
where $\tilde\varepsilon_t = \varepsilon_{1,t} - \varepsilon_{i',t} + D_{i,t}(\varepsilon_{\alpha,1} - \varepsilon_{\alpha,i'})$ and $\bm{\eta},\bm{\phi},\bm{\theta},\bm{\delta},\tilde{\bm{\phi}}$, and $\tilde{\bm{\theta}}$ are vectors containing the random effects in \eqref{random-effects} for indices $1$ and $i'$, and we take $\|\bm{a}\|_\infty = \max_j(|a_j|)$ . We will also suppose that $\|\x_{j,t}\|_\infty < M_1$ for $j \in \{1,i'\}$ and all $t = 1,\ldots,T$. Note that both $\Prob(E_1^C) \to 0$ and $\Prob(E_2^C) \to 0$  as $\sigma^2 \to 0$ with $T$ and $n$ fixed. For simplicity we will set $q_1 = q_2 = 1$.

For all $t > T^*$ let $\tilde y_{i',t}$ possess the same dynamics as $y_{i',t}$ except that this process is shifted in a manner to reflect how $y_{i,t}$ changes for all $t > T^*$. More formally, we will let 
$$
  \tilde y_{i',t} = \left\{\begin{array}{cc}
  y_{i,t} & \text{when} \; t < T^*+1; \\ 
  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}y_{1,t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t = T^* + 1; \\
  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}\tilde y_{i',t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t > T^* + 1.
\end{array}\right.	
$$
The purpose of $\tilde y_{i',t}$ is to place the post-shock responses at the same starting point which allows us to avoid strong parametric specifications on the pre-shock dynamics. This series also contains terms which are estimable from the data. Define the event 
$$
  E_3 := \{\max\left(y_{1,t},\tilde y_{i',t}\right) < M_2 : t = 1,\ldots,T\}, 
$$
where $M_2$ is chosen large enough so that $\Prob(E_3^c) \to 0$ as $\sigma^2 \to 0$. Let $M = \max(M_1,M_2).$ We now consider the recursion of $|y_{1,t} - \tilde{y}_{i',t}|$ for $t > T^*$ conditional on $E = E_1 \cup E_2 \cup E_3$, 
\begin{align*}
	&|y_{1,t} - \tilde{y}_{i',t}| 
		= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1})
		+ (\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}) 
		+ (\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t}) + \tilde\varepsilon_t| \\
	&\qquad \leq |\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}|
		+ |\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}| 
		+ |\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t})| 
		+ \varepsilon_1 \\
	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - \tilde{y}_{i',t-1}| \\
	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| \\ 
	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||\tilde{y}_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - \tilde{y}_{i',t-2}|\right\} \\
	&\qquad= \varepsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|\tilde{y}_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - \tilde{y}_{i',t-2}| \\
	&\qquad \leq \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - \tilde{y}_{i',T^*}| \\
	&\qquad = \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}|.
\end{align*}
With $T$ set, we can choose $\varepsilon_1$ small enough so that 
$
  |y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_2
$
for all $T^* < t \leq T $.

Now let $\varepsilon_3 = \max(\varepsilon_1,\varepsilon_2)$ so that 
\begin{equation} \label{bounds}
	|y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_3, \; \text{and} \; \|\x_{1,t} - \x_{i',t}\| < \varepsilon_3.
\end{equation}

Let $\tilde{\beta}$ be the OLS solution of model parameters with respect to the $\tilde{y}_{i',t}$ series, and let $\hat{\beta}$ be the OLS solution of model parameters with respect to the $y_{1,t}$ series. On $E$, these estimates will be very close to each other. We use Theorem 2.7.2 in \cite{golub1996matrix} to construct an explicit bound on $\|\tilde{\beta} - \hat{\beta}\|$. Following the notation of Section 2.7 in \cite{golub1996matrix} we will let $A$ be the design matrix with respect to the $y_{1,t}$ series so that $A\hat{\beta} = \mathbf{y}_1$ where $\mathbf{y}_1 = (y_{1,1}, \ldots, y_{1,T})'$, $\kappa(A) = \|A\|\|A^{-1}\|$ be the condition number of $A$ where $\|\cdot\|$ is a matrix norm, and we will specify that $r = \varepsilon_4 \kappa(A)$ where $\varepsilon_4$ can be chosen so that $r < 1$. We will also specify that $\varepsilon_3$ is chosen so that $\|\Delta A\| \leq \varepsilon_4\|A\|$ where $\Delta A = \widetilde{A} - A$ and $\widetilde{A}$ is the design matrix with respect to the $\tilde{y}_{i',t}$ series. Theorem 2.7.2 in \cite{golub1996matrix} states that 
\begin{equation}\label{OLSbound}
  \|\tilde{\beta} - \hat{\beta}\| \leq \frac{2\varepsilon_4}{1-r}\kappa(A)\|\hat{\beta}\|.	
\end{equation}
We can bound $\kappa(A)$ and $\hat{\beta}$ on $E$ which allows one to choose $\varepsilon_5$ so that \eqref{OLSbound} is $\|\tilde{\beta} - \hat{\beta}\| < \varepsilon_5$.

We now show that we can bound $|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}|$ for $t+h > T^*$. We restrict attention to the case where $t+h > T^*$ because when $t+h \leq T^*$ the two competing forecasts $\hat{y}_{i,t}^{1,h}$ and $\hat{y}_{i,t}^{2,h}$ are the same in our setting for all $i$. Let $t+h > T^*$, then, when $t > T^*$,
\begin{align*}
  &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| = |(\hat\eta_1 - \hat{\eta}_{i'}) + (\hat\alpha_1 - \hat\alpha_{i'}) + (\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}) + (\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t})| \\
  &\qquad \leq 2\varepsilon_5 + |\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t}| + |\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}| \\
  &\qquad \leq 2\varepsilon_5 + \|\x_{1,t}\|\|\hat{\tilde{\theta}}_1 - \hat{\tilde{\theta}}_{i'}\| + \|\hat{\tilde{\theta}}_{i'}\| \|\x_{1,t} - \x_{i',t}\| + \|\hat{y}_{1,t-1}^{1,h-1}\| |\hat{\tilde{\phi}}_1 - \hat{\tilde{\phi}}_{i'}\| + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} | \\
  &\qquad \leq 2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + \|\hat{y}_{1,t-1}^{1,h-1}\|\varepsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} |.
\end{align*}
On $E$ we can bound $|\hat{y}_{1,t-1}^{1,h-1}|$ for all $h=1,\ldots,H$ and $t=1,\ldots,T$, call this bound $M_1$. Let $\varepsilon_6 = (2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + M_1\varepsilon_5)$. Then,
\begin{align*}
  &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| \leq 2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + |\hat{y}_{1,t-1}^{1,h-1}|\varepsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
  &\qquad \leq (2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + M_1\varepsilon_5) + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
  &\qquad \leq \varepsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
  &\qquad \leq \varepsilon_6 + |\hat{\tilde{\phi}}_{i'}|\left(\varepsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}|\right) \\
  &\qquad \leq \varepsilon_6(1 + |\hat{\tilde{\phi}}_{i'}|) + |\hat{\tilde{\phi}}_{i'}|^2|\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}| \\  
  &\qquad \leq \varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h|\hat{y}_{1,t-h} - \hat{y}_{i',t-h}| \\
  &\qquad \leq \varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\varepsilon_3.  
\end{align*}
Let $\varepsilon_7 = \max_{h = 1,\ldots,H}\left(\varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\varepsilon_3\right)$ 
and conclude that 
\begin{equation} \label{forecastbounds}
  |\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| < \varepsilon_7,	
\end{equation}
for all $t = 1,\ldots,T$ and all $h=1,\ldots,H$ such that $t+h > T^*$ on the event $E$. A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made when $t+h > T^*$ and $t \leq T^*$. A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made so that $|\hat{y}_{1,t}^{2,h} - \hat{\tilde{y}}_{i',t}^{2,h}| < \varepsilon_7$.

>>>>

We first present some intermediary technical results and definitions. Let $\lambda_{\text{max},\theta_k}$, $\lambda_{\text{max},\theta_\delta}$, $\lambda_{\text{max},\gamma}$ respectively be the largest eigenvalues of $\Sigma_{\theta_k}$, $\Sigma_{\delta}$, and $\Sigma_{\gamma}$ for $k = 1,\ldots,q_2$. Define  
\begin{align*}
  \mu_{\min} &= \min\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\min(\mu_\delta),\min(\mu_{\theta_k}),\min(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \mu_{\max} &= \max\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\max(\mu_\delta),\max(\mu_{\theta_k}),\max(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
  \sigma^2_{\max} &= \max\left(\sigma^2_{\eta},\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_{\alpha},\sigma^2_{\tilde{\phi}_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right),
\end{align*}
and let $\sigma^2 = \max(\lambda_{\max}, \sigma^2_{\max})$. Now fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \epsilon_1$ for all $t$ and some choice of $\epsilon_1$. Pick some large $M > 0$. Fix $T = T_1 = T_{i'}$ and $T^* = T^*_1 = T^*_{i'}$. Define the events 
\begin{align*}
  E_1 := &\left\{\max\left(|\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \epsilon_1:\right. \\
  &\qquad j = 1,\ldots,q_1, k = 1,\ldots,q_2, t = 1,\ldots,T \left.\right\}, \\
  E_2 := &\{\|(\bm{\eta}',\bm{\phi}',\bm{\theta}',\bm{\delta}',\tilde{\bm{\phi}}',\tilde{\bm{\theta}}')'\|_\infty < M_1\},  
\end{align*}
where $\tilde\varepsilon_t = \varepsilon_{1,t} - \varepsilon_{i',t} + D_{i,t}(\varepsilon_{\alpha,1} - \varepsilon_{\alpha,i'})$ and $\bm{\eta},\bm{\phi},\bm{\theta},\bm{\delta},\tilde{\bm{\phi}}$, and $\tilde{\bm{\theta}}$ are vectors containing the random effects in \eqref{random-effects} for indices $1$ and $i'$, and we take $\|\bm{a}\|_\infty = \max_j(|a_j|)$ . We will also suppose that $\|\x_{j,t}\|_\infty < M_1$ for $j \in \{1,i'\}$ and all $t = 1,\ldots,T$. Note that both $\Prob(E_1^C) \to 0$ and $\Prob(E_2^C) \to 0$  as $\sigma^2 \to 0$ with $T$ and $n$ fixed. For simplicity we will set $q_1 = q_2 = 1$.

For all $t > T^*$ let $\tilde y_{i',t}$ possess the same dynamics as $y_{i',t}$ except that this process is shifted in a manner to reflect how $y_{i,t}$ changes for all $t > T^*$. More formally, we will let 
$$
  \tilde y_{i',t} = \left\{\begin{array}{cc}
  y_{i,t} & \text{when} \; t < T^*+1; \\ 
  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}y_{1,t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t = T^* + 1; \\
  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}\tilde y_{i',t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t > T^* + 1.
\end{array}\right.	
$$
The purpose of $\tilde y_{i',t}$ is to place the post-shock responses at the same starting point which allows us to avoid strong parametric specifications on the pre-shock dynamics. This series also contains terms which are estimable from the data. Define the event 
$$
  E_3 := \{\max\left(y_{1,t},\tilde y_{i',t}\right) < M_2 : t = 1,\ldots,T\}, 
$$
where $M_2$ is chosen large enough so that $\Prob(E_3^c) \to 0$ as $\sigma^2 \to 0$. Let $M = \max(M_1,M_2).$ We now consider the recursion of $|y_{1,t} - \tilde{y}_{i',t}|$ for $t > T^*$ conditional on $E = E_1 \cup E_2 \cup E_3$, 
\begin{align*}
	&|y_{1,t} - \tilde{y}_{i',t}| 
		= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1})
		+ (\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}) 
		+ (\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t}) + \tilde\varepsilon_t| \\
	&\qquad \leq |\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}|
		+ |\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}| 
		+ |\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t})| 
		+ \epsilon_1 \\
	&\qquad\leq (8M + 1)\epsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - \tilde{y}_{i',t-1}| \\
	&\qquad\leq (8M + 1)\epsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| \\ 
	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\epsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||\tilde{y}_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - \tilde{y}_{i',t-2}|\right\} \\
	&\qquad= \epsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|\tilde{y}_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - \tilde{y}_{i',t-2}| \\
	&\qquad \leq \epsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - \tilde{y}_{i',T^*}| \\
	&\qquad = \epsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}|.
\end{align*}
With $T$ set, we can choose $\epsilon_1$ small enough so that 
$
  |y_{1,t} - \tilde{y}_{i',t}| < \epsilon_2
$
for all $T^* < t \leq T $.

Now let $\epsilon_3 = \max(\epsilon_1,\epsilon_2)$ so that 
\begin{equation} \label{bounds}
	|y_{1,t} - \tilde{y}_{i',t}| < \epsilon_3, \; \text{and} \; \|\x_{1,t} - \x_{i',t}\| < \epsilon_3.
\end{equation}

Let $\tilde{\beta}$ be the OLS solution of model parameters with respect to the $\tilde{y}_{i',t}$ series, and let $\hat{\beta}$ be the OLS solution of model parameters with respect to the $y_{1,t}$ series. On $E$, these estimates will be very close to each other. We use Theorem 2.7.2 in \cite{golub1996matrix} to construct an explicit bound on $\|\tilde{\beta} - \hat{\beta}\|$. Following the notation of Section 2.7 in \cite{golub1996matrix} we will let $A$ be the design matrix with respect to the $y_{1,t}$ series so that $A\hat{\beta} = \mathbf{y}_1$ where $\mathbf{y}_1 = (y_{1,1}, \ldots, y_{1,T})'$, $\kappa(A) = \|A\|\|A^{-1}\|$ be the condition number of $A$ where $\|\cdot\|$ is a matrix norm, and we will specify that $r = \epsilon_4 \kappa(A)$ where $\epsilon_4$ can be chosen so that $r < 1$. We will also specify that $\epsilon_3$ is chosen so that $\|\Delta A\| \leq \epsilon_4\|A\|$ where $\Delta A = \widetilde{A} - A$ and $\widetilde{A}$ is the design matrix with respect to the $\tilde{y}_{i',t}$ series. Theorem 2.7.2 in \cite{golub1996matrix} states that 
\begin{equation}\label{OLSbound}
  \|\tilde{\beta} - \hat{\beta}\| \leq \frac{2\epsilon_4}{1-r}\kappa(A)\|\hat{\beta}\|.	
\end{equation}
We can bound $\kappa(A)$ and $\hat{\beta}$ on $E$ which allows one to choose $\epsilon_5$ so that \eqref{OLSbound} is $\|\tilde{\beta} - \hat{\beta}\| < \epsilon_5$.

We now show that we can bound $|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}|$ for $t+h > T^*$. We restrict attention to the case where $t+h > T^*$ because when $t+h \leq T^*$ the two competing forecasts $\hat{y}_{i,t}^{1,h}$ and $\hat{y}_{i,t}^{2,h}$ are the same in our setting for all $i$. Let $t+h > T^*$, then, when $t > T^*$,
\begin{align*}
  &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| = |(\hat\eta_1 - \hat{\eta}_{i'}) + (\hat\alpha_1 - \hat\alpha_{i'}) + (\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}) + (\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t})| \\
  &\qquad \leq 2\epsilon_5 + |\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t}| + |\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}| \\
  &\qquad \leq 2\epsilon_5 + \|\x_{1,t}\|\|\hat{\tilde{\theta}}_1 - \hat{\tilde{\theta}}_{i'}\| + \|\hat{\tilde{\theta}}_{i'}\| \|\x_{1,t} - \x_{i',t}\| + \|\hat{y}_{1,t-1}^{1,h-1}\| |\hat{\tilde{\phi}}_1 - \hat{\tilde{\phi}}_{i'}\| + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} | \\
  &\qquad \leq 2\epsilon_5 + M\epsilon_5 + \epsilon_3 + \|\hat{y}_{1,t-1}^{1,h-1}\|\epsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} |.
\end{align*}
On $E$ we can bound $|\hat{y}_{1,t-1}^{1,h-1}|$ for all $h=1,\ldots,H$ and $t=1,\ldots,T$, call this bound $M_1$. Let $\epsilon_6 = (2\epsilon_5 + M\epsilon_5 + \epsilon_3 + M_1\epsilon_5)$. Then,
\begin{align*}
  &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| \leq 2\epsilon_5 + M\epsilon_5 + \epsilon_3 + |\hat{y}_{1,t-1}^{1,h-1}|\epsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
  &\qquad \leq (2\epsilon_5 + M\epsilon_5 + \epsilon_3 + M_1\epsilon_5) + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
  &\qquad \leq \epsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
  &\qquad \leq \epsilon_6 + |\hat{\tilde{\phi}}_{i'}|\left(\epsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}|\right) \\
  &\qquad \leq \epsilon_6(1 + |\hat{\tilde{\phi}}_{i'}|) + |\hat{\tilde{\phi}}_{i'}|^2|\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}| \\  
  &\qquad \leq \epsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h|\hat{y}_{1,t-h} - \hat{y}_{i',t-h}| \\
  &\qquad \leq \epsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\epsilon_3.  
\end{align*}
Let $\epsilon_7 = \max_{h = 1,\ldots,H}\left(\epsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\epsilon_3\right)$ 
and conclude that 
\begin{equation} \label{forecastbounds}
  |\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| < \epsilon_7,	
\end{equation}
for all $t = 1,\ldots,T$ and all $h=1,\ldots,H$ such that $t+h > T^*$ on the event $E$. A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made when $t+h > T^*$ and $t \leq T^*$. A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made so that $|\hat{y}_{1,t}^{2,h} - \hat{\tilde{y}}_{i',t}^{2,h}| < \epsilon_7$.

We now bound the difference in loss differential vectors $\|\dbf_{1,t} - \dbf_{i',t}\|$ for $t > T^*$. What we have showed so far in \eqref{bounds} and \eqref{forecastbounds} allows us to write
\begin{equation} \label{L1bound}
  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{1,h}_{i',t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{i',t}| + 2(\epsilon_3 + \epsilon_7).
\end{equation}
We conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \epsilon_8$ on $E$ for all $t > T^*$ where $\epsilon_8$ is chosen so that \eqref{L1bound} holds when $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \epsilon_8$ on $E$ for all $t > T^*$.
%when we specify the loss $L(a,b) = |a-b|$. The loss differential vector $\dbf_{1,t} \in \R^H$ has elements $|y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}|$. What we have showed so far in \eqref{bounds} and \eqref{forecastbounds} allows us to write
%$$
%  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{1,h}_{i',t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{i',t}| + 2(\varepsilon_3 + \varepsilon_7).
%$$
%Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.
Putting this all together, we can pick $\epsilon_8$ small enough so that for some fixed $\epsilon > 0$,
\begin{equation} \label{testbounds}
   \left|\sqrt{T}\frac{\textbf{w}_1'\bar{\dbf}_1^b - \textbf{w}_1'\bar{\dbf}_1}{\hat{\zeta}^b_1} - \sqrt{T}\frac{\textbf{w}_{i'}'\bar{\dbf}_{i'}^b - \textbf{w}_{i'}'\bar{\dbf}_{i'}}{\hat{\zeta}^b_{i'}}\right| < \epsilon	
\end{equation}
on the set $E$ where we specify that $\textbf{w}_1 = \textbf{w}_{i'}$ and that the MBB procedures samples the same indices of blocks from $\dbf_{1,t}$ and $\dbf_{i',t}$, $t = T^*+1,\ldots, T$ when forming the test statistics in \eqref{testbounds}. Thus for any fixed small $\epsilon < 0$ there exists a choice of $\sigma^2$ and $\epsilon_1$ such that inferences involving the $i'$ series for which post-shock behavior is observed can be substituted in place of the $i = 1$ series under study with high probability of a correspondence in inferences.
